Supplementary Information

### 2021-01-29 doc/manuscript/MEE_manuscript.Rmd
knit in decadal plots
#104

decadal_analysis_figs_all = "S32-SXX"
decades_figure_ZOF= "SXX"

@@

@@

In a few instances, directional changes in growth are likely attributable to abiotic drivers.
In the Czech Republic (ZOF), acid deposition dramatically reduced growth in  *(DECADES)* [**REFS**], as captured in our records (Fig. `r decades_figure_ZOF`), and *this influenced linear growth trends of different species in differently within the GLS model*. 
In cases such as this, a non-linear response function to $year$, or incorporation of data on pollution, would be needed to accurately characterize changing growth trends, but that is beyond the scope of the current anlaysis.
In New Mexico (LT), *we suspect that a strong drying trend is not fully captured by the dominant climate drivers (?).*
At Scotty Creek, rapid warming and melting permafrost are altering hydraulic conditions, resulting in growth declines, high mortality, and low recruitment of *Picea mariana* [@sniderhan_growth_2016; @dearborn_permafrost_2020].

>>>>

decadal_analysis_figs_all = "S32-S41"
decadal_plot_BCNM = "S32"
decadal_plot_HKK = "S33"
decadal_plot_SCBI = "S34"
decadal_plot_LDW = "S35"
decadal_plot_HF = "S36"
decadal_plot_ZOF = "S37"
decadal_plot_NIO = "S38"
decadal_plot_LT = "S39"
decadal_plot_CB = "S40"
decadal_plot_SC = "S41"

@@

decadal_plot_BCNM_legend = "Figure. S32. (Decadal BCNM)"
decadal_plot_HKK_legend = "Figure. S33. (Decadal HKK)"
decadal_plot_SCBI_legend = "Figure. S34. (Decadal SCBI)"
decadal_plot_LDW_legend = "Figure. S35. (Decadal LDW)"
decadal_plot_HF_legend = "Figure. S36. (Decadal HF)"
decadal_plot_ZOF_legend = "Figure. S37. (Decadal ZOF)"
decadal_plot_NIO_legend = "Figure. S38. (Decadal NIO)"
decadal_plot_LT_legend = "Figure. S39. (Decadal LT)"
decadal_plot_CB_legend = "Figure. S40. (Decadal CB)"
decadal_plot_SC_legend = "Figure. S41. (Decadal SC)"

@@

In a few instances, directional changes in growth are likely attributable to abiotic drivers.
In the Czech Republic (ZOF), acid deposition dramatically reduced growth in  *(DECADES)* [**REFS**], as captured in our records (Fig. `r decadal_plot_ZOF`), and *this influenced linear growth trends of different species in differently within the GLS model*. 
In cases such as this, a non-linear response function to $year$, or incorporation of data on pollution, would be needed to accurately characterize changing growth trends, but that is beyond the scope of the current anlaysis.
In New Mexico (LT), *we suspect that a strong drying trend is not fully captured by the dominant climate drivers (?).*
At Scotty Creek, rapid warming and melting permafrost are altering hydraulic conditions, resulting in growth declines, high mortality, and low recruitment of *Picea mariana* [@sniderhan_growth_2016; @dearborn_permafrost_2020].

### 2021-01-29 doc/manuscript/MEE_manuscript_SI.Rmd
knit in decadal plots
#104

@@

>>>>

#decadal plots
do.call(file.remove, list(list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/decadal_plots/", full.names = TRUE))) # first remove old files
flist <- list.files("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/tree-rings_global-change/decadal_plots/", full.names = TRUE)
file.copy(flist, "/Users/kteixeira/Dropbox (Smithsonian)/GitHub/EcoClimLab/ForestGEO-climate-sensitivity/doc/manuscript/tables_figures/SI_figures/decadal_plots/")

@@

\newpage
## `r decadal_plot_BCNM_legend`

![`r decadal_plot_BCNM_legend`](tables_figures/SI_figures/decadal_plots/BCI.png){ width=100% }

\newpage
## `r decadal_plot_HKK_legend`

![`r decadal_plot_HKK_legend`](tables_figures/SI_figures/decadal_plots/HKK.png){ width=100% }

\newpage
## `r decadal_plot_SCBI_legend`

![`r decadal_plot_SCBI_legend`](tables_figures/SI_figures/decadal_plots/SCBI.png){ width=100% }
\newpage
## `r decadal_plot_LDW_legend`

![`r decadal_plot_LDW_legend`](tables_figures/SI_figures/decadal_plots/LD.png){ width=100% }

\newpage
## `r decadal_plot_HF_legend`

![`r decadal_plot_HF_legend`](tables_figures/SI_figures/decadal_plots/HF.png){ width=100% }

\newpage
## `r decadal_plot_ZOF_legend`

![`r decadal_plot_ZOF_legend`](tables_figures/SI_figures/decadal_plots/ZN.png){ width=100% }

\newpage
## `r decadal_plot_NIO_legend`

``` {r eval=FALSE}
![`r decadal_plot_NIO_legend`](tables_figures/SI_figures/decadal_plots/NIO.png){ width=100% }
```

\newpage
## `r decadal_plot_LT_legend`

![`r decadal_plot_LT_legend`](tables_figures/SI_figures/decadal_plots/NM.png){ width=100% }

\newpage
## `r decadal_plot_CB_legend`

![`r decadal_plot_CB_legend`](tables_figures/SI_figures/decadal_plots/CB.png){ width=100% }
\newpage
## `r decadal_plot_SC_legend`

![`r decadal_plot_SC_legend`](tables_figures/SI_figures/decadal_plots/SC.png){ width=100% }
